---
title: "Module 12 Markdown Functions"
output:
  html_document:
    df_print: paged
---
# Tenative Functions

This document contains, as requested by the assignment, a series of *tenative* functions for R programing in relation to the final project that has been assigned for the course. Especially since I have not had my proposal for the project confirmed yet, I wisht to stress these are all works in progress and in need of further refinement.  
The idea behind the functions is that the functions will be able to be fed a dataset purporting to represent a fictional gym and the daily uses of various resources in the gym over the course of a year for a five year period. The first function should allow for the generation of a yearly mean, with the second hopefully allowing for a mean of all the years for a service at once. The final function that I have currently written would hopefully allow me to take the means for each year for each topic/data and then convert them into per-year graphs, allowing for the data to be visually presented.   

# Non-visual functions  

## Various Services Use per Day by Year    
```{r}
DailyUsePerYearMean<-function(x){
  x2030<-mean(x[7:20])
  x2031<-mean(x[9:21])
  x2032<-mean(x[5:15])
  x2033<-mean(x[6:19])
  x2034<-mean(x[8:19])
  XDailyYearlyMeans<-cbind(x2030, x2031, x2032, x2033, x2034)
  print(XDailyYearlyMeans)
}```  

## Generating Means for all columns  
```{r}
TheMeanColumnTotal<-function(x){
  TheMeanColumnTotal<-colMeans(x)
}```  


# Visualization Tools  

## Graphing Service Means by Year  
```{r}
DailyUsesChart<-function(x){
  M1<-DailyUsePerYearMean(x[,1])
  M2<-DailyUsePerYearMean(x[,2])
  M3<-DailyUsePerYearMean(x[,3])
  M4<-DailyUsePerYearMean(x[,4])
  M5<-DailyUsePerYearMean(x[,5])
  M6<-DailyUsePerYearMean(x[,6])
  barplot(M1, col = "black", main= "Member Sign-In Terminal Daily Use: Yearly Mean", xlab="Years")
  barplot(M2, col = "darkolivergreen1", main= "Daily Use of Bodybuilding Equipment: Yearly Mean", xlab="Years")
  barplot(M3, col = "darkorchid1", main= "Daily Personal Trainer Appointments: Yearly Mean", xlab="Years")
  barplot(M4, col = "firebrick1", main= "Daily Attendence of Children's Fitness class: Yearly Mean", xlab="Years")
  barplot(M5, col = "gold", main= "Daily Use of Aerobics Equipment: Yearly Mean", xlab="Years")
  barplot(M6, col = "hotpink", main= "Daily Use of Sign-In sheet for pool: Yearly Mean", xlab="Years")
}```  


When you click the **Knit** button a document will be generated that includes both content as well as the output of any embedded R code chunks within the document. 